Markov Link Method for calibrating without joint measurement, including the case of destructive measurements

### 2018-05-15 paper/paper.tex
added qhat figure

>>>>

\begin{figure}
\includegraphics[width=0.8\textwidth]{../images/qhat}
\caption{The $\hat q$ estimated by the MLM method with $\kappa=.1$.  Here we find that the calibration is largely diagonal.  That is, for the most part, if a cell-type was designated as a particular type according to one method, we expect it to be designated by the same type in the other method.  However, there are some striking deviations from diagonality.  Note that the number of cell-types is not exactly the same between the two methods, but this provides no barrier to implementin the MLM method.   The final row and column are in some sense ``miscellaneous'' and can be disregarded to some extent.\label{fig:allenout}}
\end{figure}
